signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-18 paper.tex
slightly improved descriptions
improved comparision of encodings
fixed awful msitake - confused the best and the worst encodings

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/reglen.png}
\caption{A) Distribution of lengths of signal peptides. B) Distribution of the lengths of signal peptide regions. The measure of the length is a number of amino acids in the subsequence. The data was extracted from 2~589 signal peptide sequences derived from UniProt database (see \textbf{Data selection} in \textbf{Methods}).}
\label{fig:reglen}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9687, MCC = 0.8689). 2. An encoding providing the best specificity (AUC = 0.9346, MCC = 0.6479).}
\label{fig:cvres}
\end{figure}

@@

\begin{table}[ht]
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, E, K, Q, R \\ 
   \rowcolor[gray]{0.85}D, G, N, P, S, T \\ 
  C, H, I, L, M, V \\ 
   \rowcolor[gray]{0.85}F, W, Y \\ 
   \bottomrule
\end{tabular}
\caption{Best-sensitivity (final) encoding.} 
\label{tab:best}
\end{minipage}
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
D, E, H, K, N, Q, R \\ 
   \rowcolor[gray]{0.85}G, P, S, T, Y \\ 
  F, I, L, M, V, W \\ 
   \rowcolor[gray]{0.85}A, C \\ 
   \bottomrule
\end{tabular}
\caption{Worst-sensitivity encoding.} 
\label{tab:worst}
\end{minipage}
\end{table}

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/enccomp.png}
\caption{A comparision of encodings.}
\label{fig:enccomp}
\end{figure}

>>>>

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/reglen.png}
\caption{A) Distribution of lengths of signal peptides. B) Distribution of the lengths of signal peptide regions. The measure of the length is a number of amino acids in the subsequence. The data was extracted from 2~589 signal peptide sequences derived from UniProt database (see \textbf{Data selection} in \textbf{Methods}).}
\label{fig:reglen}
\end{figure}

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9687, MCC = 0.8689). 2. An encoding providing the best specificity (AUC = 0.9346, MCC = 0.6479).}
\label{fig:cvres}
\end{figure}

@@

The best and the worst encoding share some similarities. The both groupings have strongly pronounced highly hydrophobic group 3 (see Table~\ref{tab:best}, Table~\ref{tab:best} and Figure~\ref{fig:enccomp}.

\begin{table}[ht]
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
D, E, H, K, N, Q, R \\ 
   \rowcolor[gray]{0.85}G, P, S, T, Y \\ 
  F, I, L, M, V, W \\ 
   \rowcolor[gray]{0.85}A, C \\ 
   \bottomrule
\end{tabular}
\caption{The best sensitivity (final) encoding.} 
\label{tab:best}
\end{minipage}
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, E, K, Q, R \\ 
   \rowcolor[gray]{0.85}D, G, N, P, S, T \\ 
  C, H, I, L, M, V \\ 
   \rowcolor[gray]{0.85}F, W, Y \\ 
   \bottomrule
\end{tabular}
\caption{The worst sensitivity encoding.} 
\label{tab:worst}
\end{minipage}
\end{table}

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/enccomp.png}
\caption{A comparision of encodings. A) Properties of amino acids in the best and the worst sensitivity encoding. B) Frequencies of amino acids beloning to the encodings in regions of signal peptide and mature protein.}
\label{fig:enccomp}
\end{figure}
